Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-23 writing/embedded_meta_learning_appendix.tex
Clarifying hold-outs

@@

Note that there are two kinds of hold-out in the training of this system. First, some of the trained tasks are held-out on each training step (i.e. $D_2$), in order to force the system to generalize rather than just memorize. Second, there are truly held-out tasks that the system has never seen in training, these are the held-out tasks and meta-mappings that we evaluate on at the end of training. \par

>>>>

\subsection{Clarifying hold-outs} \label{app_clarifying_holdouts}
There are several distinct types of hold-outs in the basic training of our architecture:
\item On each basic task, some of the data ($D_1$) is fed to the meta-network $\mathcal{M}$ while some ($D_2$) is held out. This encourages the model to actually infer the underlying function, rather than just memorizing the examples.
\item There are also truly held-out tasks that the system has never seen in training. These are the held-out tasks that we evaluate on at the end of training and report results.
This applies analogously to the meta-mappings: each time a meta-mapping is trained, some basic tasks are used as examples while others are held out to encourage generalization. There are also meta-mappings which have never been encountered during training, and those are the meta-mappings we evaluate on at hte end of training. We also evaluate the old (and new) meta-mappings on the new basic tasks that have never been trained.

@@

Note that there are three kinds of hold-out in the training of this system, see section 
ref{app_clarifying_holdouts}. \par
